Investigating the Gaussianity of Supernova SALT2 Summary Statistics

### 2016-08-09 dessn/investigations/gaussianity/paper/gaussianity.tex
Adding a ton of citations from betoule for potential use

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

Few sentences on cosmology.

@@

Thus motivation

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\blue}{\color{blue}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the years since the discovery of the acceleration of our universe \citep{RiessFilippenko1998, SchmidtSuntzeff1998, PerlmutterAldering1999}, supernova cosmology continued to grow as an important cosmological probe. Recent supernova studies offer far greater statistical power than ever before, systematics are better understood, and the very phenomenon of supernova are described with improved models \citep{GuyAstier2007, ConleyGuy2011, BetouleKessler2014, RubinAldering2015}.

\vspace{10mm}

SNLS \citep{AstierGuy2006, SullivanGuy2011}

ESSENCE \citep{WoodVaseyMiknaitis2007}

Pan-STARRS \citep{TonryStubbs2012, ScolnicRest2014, RestScolnic2014}

SDSS-II \citep{FriemanBassett2008, KesslerBecker2009, SollermanMortsell2009, LampeitlNichol2010, CampbellDAndrea2013}

Harvard-Smithsonian Center for Astrophysics survey \citep[CfA,][]{HickenChallis2009}

Carnegie Supernova Project \citep[CSP,][]{ContrerasHamuy2010, FolatelliPhillips2010, StritzingerPhillips2011}

Lick Observatory Supernova Search \citep[LOSS,][]{GaneshalingamLi2013}

Nearby Supernova Factory \cite[SNF,][]{AlderingAdam2002}

HST used in \citep{RiessStrolger2007, SuzukiRubin2012}

Modern results systematic limited \citep{ConleyGuy2011, SuzukiRubin2012, ScolnicRest2014}

Efforts overcome \citep{IvezicSmith2007, RegnaultConley2009, TonryStubbs2012}

DES

Compilations:

Suzuki 2012: Union 2.1
For citing SALT2, cite Guy2007, Guy2010, Mosher2014

{\blue
Few sentences on cosmology.

@@

Thus motivation}
